\documentclass{article}

\title{Study Guide for UX Study on Mumble Client}
\author{Timothy Heath}
\date{\today}

\begin{document}
    \maketitle
    \tableofcontents
    \section{How the study trial will be conducted}
    The study will be conducted by having the user sit down in front of a virtual machine.
    Using a virtual machine like this will allow the study to be run from any computer, only the recording software \emph{might}
    need to run on the host. The virtual machine will be preconfigured to run murmurd with mumble client installed.
    This way the user need only open the mumble client to begin the study.
    \section{Where the study trial will be conducted}
    The study will be conducted at home, at the SVSU Library, or in the classroom.
    \section{Traits of an ideal trial participant}
    The traits of an ideal trial participant are enumerated as follows:
    \begin{itemize}
        \item Uses voice chat services in daily life
        \item Uses text chat services in daily life
        \item Is familiar with mouse
        \item Is familiar with keyboard
        \item Is accustomed to hitting the windows button to get a run menu
        \item Is accustomed to desktop icons
        \item Is able to read basic sentences
        \item Is used to having everything mostly set up for himself
    \end{itemize}
    \section{Recording plan}
    The screen of the virtual machine will be recorded for the duration of the test, this will
    be done automatically and saved to a file (filename including time and date information to
    prevent overwriting). A USB camera will be set up to record the user from the front. Further
    all microphone input and system audio output will be recorded, the microphone recording the user.
    \section{Requirements for study}
    \begin{itemize}
        \item A host computer running MS Windows, OS X, GNU/Linux, or a BSD.
        \item Virtual Box software installed on a host computer.
        \item A USB Microphone
        \item A USB Camera
        \item Gnome based interface running on the vm image via Linux
        \item Mumble Client installed on the vm image
        \item Murmur Server installed on the vm image
        \item Automatic recording  on boot configured on the vm image
        \item virtual box host configured to pass through the usb devices
    \end{itemize}
    \section{Participant script}
    Welcome, thank you for participating in our study today. Shortly I will
    give you some tasks to complete using the Mumble Client. But, before I
    do this, there are some things that I need to cover with you.

    First, because the study examines how you interact with the software,
    audio and video of you, and the monitor will be recorded for later
    review. From this point forward, you will be recorded.

    [Begin recording]

    Second, it is imperitive that you understand, you are not being tested.
    You cannot fail this study. Difficulty or failure in completion of a
    task reflects not on yourself, but on the Mumble Client. We are not
    interested in how you go about trying to use the Mumble Client. We will
    gain useful information regardless of whether or not you find the Mumble
    Client easy to use. Do you understand?

    [Allow the participant to respond]

    Good, and your name is?

    [Allow the participant to respond]

    Thank you

    My name is [Your name].

    Our study focuses on the Mumble Client software. Have you ever used Mumble before?

    [If yes, then engage in dialog about the Mumble Client]
    [If not, then ask whether the user has ever heard of the Mumble Client]
    [If the user has not even heard of it, just explain that it is generic voice and text chatting software]
\end{document}
